### 2018-05-31 manuscript/visualdesign.tex
figure done

\begin{itemize}
\item \textit{Effective multivarible cross-filter for individual characteristics (C1)}: there are eight domains to describe an individual. The system is supposed to provide a straright-forward way for easy filtering by the eight criteria.
\item \textit{Good overview of the multivarible individuals (C2)}: following the visual analytics manta by Shneiderman~\cite{RN459}, it is very important to provide a good overview of all the individuals then the users know where to explore. 
\item \textit{Intuitive perception of an individual as an organic complex (C3)}: the system should make use of users' daily life experience in knowing people to provide intuitive visualization, instead of the lifeless representation by number. The visual design needs to help end-users to pick desirable ones from the mass.  
\item \textit{Compact visualization of mobility patterns in the constraint of spatial space (C4)}: the analysis of mobility patterns include multivariables, including the conventional spatial and temporal dimensions, as well as other dimensions, e.g., travel demands, frequency, etc. The system should handle a compact layout to make the correlation between spatial and abstract information easily. 
\item \textit{Flexible interactions to explore the mobility patterns within one group or between groups (C5)}: since the system needs to support the comparison among groups, \textit{Task 3} \m{TO BE WRITTEN...}
\end{itemize}

@@

With those design considerations, we develop a visual analytics system as Figure~\ref{fig:teaser} shows. It composes of individual panel to explore and identify groups (\textit{Task 1}) and spatial panel to explore and compare the mobility pattern (\textit{Task 2 and 3}). 
% Semantic understanding of social characteristics.

@@

Glyph-based visualization~\cite{borgo2013glyph} is the form of visual design to compose multivaribles into a collection of unified visual symbols, known as glyph. Glyph is intended for quick understanding and aligned comparison. Among glyph design, Chernoff Face~\cite{chernoff1973use} represents data variabules by the different features of a cartoon face. Following the idea of Chernoff Face~\cite{chernoff1973use}, we design a type of glyph, a graphical representation of people with specific demographic characteristics. The idea behind using faces is that humans easily recognize faces and notice small changes without difficulty (\textit{C3}). Those visual profiles are intended for intutive visual understanding and clustering, to abstract to concrete and semantic understanding, to help users clues to target the interested individual groups effectively.

Figure~\ref{fig:design_profile} shows the legend for the user profile. Those design dimensions are driven by data.The eight demographic dimensions are systematically designed into different visual symbols. Considering there are two types of variables, i.e., the numeric attributes and categorical attributes. By different composition, stimulus pattern which has the abstract deomgraphic measurement of individuals.

\begin{itemize}
\item \textbf{Gender} the gender is visually mapped to the hair style of the avatar. 
\item \textbf{Age} age is implied by the decoration on the hair. For the elder above 70, the hair is dyed to gray. For the youth beneath 18, hair decoration for girls and boys are adapted to the hair style.
\item \textbf{Education} The thickness of eye glasses is used to indicate the different levels in education.
\item \textbf{Job} The clothes is designed to imply the job of the individual. There are 9 types of clothes.
\item \textbf{Belongings} for house, car, residential license are considered as the belongings to the individual, so we design each of them as an add-on decoration to imply whether the individual has it or not.
\item \textbf{Income} a money symbol is used to show the different income levels.
\end{itemize}

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/design_profile}
 \caption{Design Profile}
 \label{fig:design_profile}
\end{figure}

With the visual mapping, the profiles varies from individual to individual. By concretizing the attributes which otherwise is too abstract to percept, users can scan and search for interesting target organically in figures. For example, Figure~\ref{fig:div_example} lists the top profiles filtered by jobs, in descending order. Textual number beneath the profile is the number of individual with same characteristics. It is found that the majority of workmen earn low and have no residential license. For the officers, all of them have residential licensemost and most of them has house. Some of retired people are in old age. Most of managers are at undergraduates, even graduates.

@@

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/design_example}
 \caption{Top filtered profiles categoriesd job}
 \label{fig:div_example}
\end{figure}

>>>>

\begin{itemize}
\item \textit{Effective multivarible cross-filter for individual characteristics (C1)}: there are eight domains to describe an individual. The system is supposed to provide a straright-forward way for easy filtering by the eight criteria.
\item \textit{Good overview of the multivarible individuals (C2)}: following the visual analytics manta by Shneiderman~\cite{RN459}, it is very important to provide a good overview of all the individuals then the users know where to explore. 
\item \textit{Intuitive perception of an individual as an organic complex (C3)}: the system should make use of users' daily life experience in knowing people to provide intuitive visualization, instead of the lifeless representation by number. The visual design needs to help end-users to pick desirable ones from the mass.  
\item \textit{Compact visualization of mobility patterns in the constraint of spatial space (C4)}: the analysis of mobility patterns not only includes the conventional spatial and temporal dimensions, but also other abstract dimensions, e.g., travel purpose, visiting frequency, etc. The system should handle a compact layout to support the easy correlation between spatial and abstract information. 
\item \textit{Flexible interactions to explore the mobility patterns either within one group or between groups (C5)}: to support the comparison among groups, \textit{Task 3}, the system should maintains flexbile interactions which allows the end-users to explore freely.
\end{itemize}

@@

With those design considerations, we develop a visual analytics system as Figure~\ref{fig:teaser} shows. It composes of individual panel to explore and identify groups (\textit{Task 1}) and spatial panel to explore and compare the mobility pattern (\textit{Task 2 and 3}). \m{EXPAND...}
% Semantic understanding of social characteristics.

@@

Glyph-based visualization~\cite{borgo2013glyph} is the form of visual design to compose multivaribles into a collection of unified visual symbols, known as glyph. Glyph is intended for quick understanding and aligned comparison. Among glyph design, Chernoff Face~\cite{chernoff1973use} represents data variabules by the different features of a cartoon face. Following the idea of Chernoff Face, we design a type of glyph, a graphical representation of people with specific individual characteristics. The idea behind using faces is that humans easily recognize faces and notice small changes without difficulty (\textit{C3}). Those visual profiles are intended for intutive visual understanding, from abstract to concrete and semantic understanding, to support users to target the interested individual groups effectively.

Figure~\ref{fig:design_profile} shows the legend for the user profile. The eight domains are encoded by visual symbols and organically organized in a human figure. There are bascially three types of variables to drive the figure, i.e., the numeric, categorical and boolean ones. For numeric attributes such as income and education levels, visual symbol keeps consistent design but with changing visual variation, such as size, thickness. For the categorical attributes such as job, visual symbols are designed seperately for better semantic meaning. For the boolean attribute like car, house, a symbol is designed to indicate its existence. With this consideration, the eight domains are designed as following:

% For numeric attributes.

% By different composition, stimulus pattern which has the abstract deomgraphic measurement of individuals.

\begin{itemize}
\item \textbf{Gender} the gender is visually mapped to the hair style of the avatar. 
\item \textbf{Age} age is implied by the decoration on the hair. For the elder above 70, the hair is dyed to gray. For the youth beneath 18, a hair decoration is adapted for the different hair styles of girls and boys.
\item \textbf{Education} The thickness of eye glasses is used to indicate the different levels in education.
\item \textbf{Job} The clothes is designed to imply the job of the individual. There are 9 types of clothes.
\item \textbf{Belongings} for real estate, car, residential license are considered as the belongings to the individual, so we design each of them as an add-on decoration to imply whether the individual has it or not.
\item \textbf{Income} a money symbol is used to represent the income, whose size encodes the income level. The more money an individual earns, the larger the symbol is.
\end{itemize}

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/design_profile}
 \caption{Design Profile: the eight characteritical domains are encoded and organized in an organic human figure.}
 \label{fig:design_profile}
\end{figure}

With the visual mapping, the profile varies from individual to individual. By concretizing the attributes which otherwise is too abstract to percept, users can scan and search for interesting target effectively. Figure~\ref{fig:div_example} lists the figures with the top 10 largest population in some job. The textual number beneath indicates the population. It is found that the majority of workmen earn low salary and most of them have no residential license. On the contrary, for the officers, all of them have residential license and most of them has house. Some of the retired people are in old age. Most of managers are at undergraduates, even graduates.

@@

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/design_example}
 \caption{Representative figures with the top 10 largest population in four jobs}
 \label{fig:div_example}
\end{figure}
